An Experimental Evaluation of Hybrid Vector Search (EA\&B)

### 2025-04-15 VLDB2026/main.tex
change vectordb range filter robustness

Among vector databases, Milvus performed well. PASE was not included in this round of tests because it does not support datasets with dimensions over 512 and performed poorly in earlier experiments.

>>>>

Among vector databases, Milvus performed well. VBASE is sensitive to datasets and achieved recall below 0.8 on Text2Image. PASE was excluded from this round of tests because it does not support datasets with dimensions over 512 and performed poorly in earlier experiments.
